Tropical mathematics and the Lambda-calculus I

### 2023-08-02 CSL24/appSection5.tex
commit

\subsection{Section~\ref{sec:3B}: the language $\BSTLC$}

In Section 4 we considered a variant $\BSTLC$ of $\STLC$ with linear simple types and a graded exponential $!_{n}A$, for all $n\in \BB N$, corresponding to a somehow simplified version of the language $\mathrm{Fuzz}$ \cite{Reed2010}. 
%The terms are generated by the grammar:
%
%{
%\begin{minipage}{\textwidth}
%\begin{align*}
%M:= x\mid \lambda x.M\mid MM \mid !M \mid \mathsf{let}\  !x=M \ \mathsf{in}\  M%\mid (t,u)\mid  \mathsf{let}\  (x,y)=t \ \mathsf{in} \  u 
%\end{align*}\end{minipage}}\medskip\\
%For the purposes of this article we limited ourselves to a minimal fragment of this language. For a more practical language see \cite{Reed2010,Gaboardi2017}.

The types are generated by the grammar below:

{
\begin{minipage}{\textwidth}
\begin{align*}
A:= X \ \mid  \ !_{n}A \multimap A
\end{align*}\end{minipage}}\medskip\\
Type judgements are of the form $\Gamma \vdash t:A$, where a context $\Gamma$ is a list of declarations of the form $x :_{n}A$, with $n\in \BB N$.
We define the following operation $\Gamma+\Delta$  as follows:

{
\begin{minipage}{\textwidth}
\begin{align*}
() + () & =() \\
(\Gamma, x:_{m} A)+( \Delta, x:_{n} A) & =  (\Gamma+\Delta), x:_{m+n}A \\
(\Gamma, x:_{n}A)+\Delta & =(\Gamma+\Delta), x:_{n}A \qquad (x\notin \Delta) \\
\Gamma+ (\Delta, x:_{n}A) &= (\Gamma+\Delta), x:_{n} A \qquad (x\notin \Gamma)
\end{align*}\end{minipage}}\medskip\\
Moreover, we let $m\Gamma$ be the context made all judgements $x:_{mn}A$, where $(x:_{n}A): \Gamma$.

The typing rules of $\BSTLC$ are illustrated in Fig.~\ref{fig:fuzz}.

%Observe that one can always type an affine term like e.g.~$\lambda xy.x$ with a linear type $A\multimap B\multimap A$. Instead, a term like $\lambda xy.x(xy)$ containing two occurrences of $x$ cannot be given the linear type $(A\multimap A)\multimap (A\multimap A)$ but a type of the form
%$!_{2}(A\multimap A)\multimap (A\multimap A)$.

\begin{figure}
\fbox{
\begin{minipage}{0.9\textwidth}
\begin{center}

  {
\AXC{}
\UIC{$ x:_{1}A\vdash x: A$}
\DP}

\bigskip

\begin{tabular}{c c }
\AXC{$\Gamma \vdash M:A$}
\UIC{$\Gamma, x:_{0}B \vdash M:A$}
\DP

&

\AXC{$\Gamma, x:_{n}B, y_{m}:B\vdash M:A$}
\UIC{$\Gamma, x:_{n+m}B\vdash M[x/y]:A$}
\DP

\\

&

\\

  {
\AXC{$\Gamma, x:_{n} A\vdash M: B$}
\UIC{$\Gamma\vdash \lambda x.M: !_{n}A\multimap B$}
\DP}

&

  {
\AXC{$\Gamma \vdash M: A\multimap B$}
\AXC{$\Delta\vdash N: A$}
\BIC{$\Gamma +\Delta\vdash MN: B$}
\DP}
\\

%&

%\\
%
%  {
%\AXC{$\Gamma \vdash t\in A$}
%\AXC{$\Delta \vdash u\in B$}
%\BIC{$\Gamma+\Delta \vdash ( t,u) \in A\otimes B$}
%\DP}
%
%& 
%
%
%  {
%\AXC{$\Gamma\vdash t\in A \otimes B$}
%\AXC{$\Delta,x\in_{n}A, y\in_{n} B\vdash u:C$}
%\BIC{$n\Gamma+\Delta \vdash \mathsf{let}\  (x,y)=t \ \mathsf{in}  \ u\in C$}
%\DP}
%\\
%&

%\\
%
%
%
%
%
%& 
%
%  {
%\AXC{$\Gamma\vdash M: !_{n}A$}
%\AXC{$\Delta,x\in_{mn}A\vdash u:C$}
%\BIC{$m\Gamma+\Delta \vdash \mathsf{let}\  !x=M \ \mathsf{in} \ u :  C$}
%\DP}

\end{tabular}

\bigskip

  {
\AXC{$\Gamma \vdash M: A$}
\UIC{$n\Gamma \vdash M : \ !_{n}A$}
\DP}

\end{center}
\end{minipage}
}
\caption{Typing rules for $\BSTLC$.}
\label{fig:fuzz}
\end{figure}

\subsection{Proofs from Section~\ref{sec:3B}: $(\LREL, !_{n})$ is a model of $\BSTLC$}

>>>>

%\subsection{Proofs from Section~\ref{sec:3B}: $(\LREL, !_{n})$ is a model of $\BSTLC$}
